\jaxcosmo: End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2022-06-01 paper.tex
minor update

Currently, \jaxcosmo\  implements the \cite{Eisenstein_1998} transfer function and non-linear features through the \textit{halofit} model by \cite{2012ApJ...761..152T} or \cite{2003MNRAS.341.1311S} (w/o the neutrino contribution introduced by \cite{10.1111/j.1365-2966.2011.20222.x}). It is worth to mention that to perform \textit{autodiff} we have implemented a series of tools as differentiable ODE (Romberg algorithm) as well as integration quadrature (eg. Simpson).

>>>>

Currently, \jaxcosmo\  implements the \cite{Eisenstein_1998} transfer function and non-linear features through the \textit{halofit} model by \cite{2012ApJ...761..152T} or \cite{2003MNRAS.341.1311S} without the neutrino contribution introduced by \cite{10.1111/j.1365-2966.2011.20222.x}. No baryonic feedback is considered yet. It is worth to mention that to perform \textit{autodiff} we have implemented a series of tools as differentiable ODE via Runge-Kutta as well as integration methods as Simpson quadrature and Romberg algorithm.
